\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-07-23 manuscript/manuscript.tex
updated authorship

% Useful packages
\usepackage{amsmath, graphicx, multicol, booktabs, float, abstract, placeins, mathtools, chngcntr}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

% Title
\title{
    \usefont{OT1}{bch}{b}{n}
    \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt]
    \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\
}
\selectlanguage{english}
\usepackage{authblk}
\author[1]{Eddie Guo}
\author[2]{Mehul Gupta}
\author[1]{Pouria Torabi}
\author[2]{Sunand Kannappan}
\affil[1]{University of Alberta}
\affil[2]{University of Calgary}

@@

% Acknowledgements
\section*{Acknowledgements}
We wish to acknowledge the STEM Fellowship for organizing the 2020 Big Data Challenge, as well as Roche, SAS, Canadian Science Publishing, Digital Science, Altmetric, and Overleaf for their contributions that enabled this competition. We would like to thank our mentor, Dr. Daiva Nielsen for her feedback on our paper. We would also like to acknowledge Matthew Pietrosanu, Stephen Styles, Danyi Liu, and Boya Peng for their critical statistical review of the manuscript draft.

\bibliography{bibliography}

>>>>

% Useful packages
\usepackage{amsmath, graphicx, multicol, booktabs, float, abstract, placeins, mathtools, chngcntr}
\usepackage[numbers	]{natbib}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

% Title
\title{
    \usefont{OT1}{bch}{b}{n}
    \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt]
    \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\
}
\selectlanguage{english}
\usepackage{authblk}
\author[1]{Eddie Guo}
\author[1]{Pouria Torabi}
\author[2]{Daiva Nielsen}
\author[3]{Matthew Pietrosanu}
\affil[1]{\small Neuroscience and Mental Health Institute, University of Alberta}
\affil[2]{\small School of Human Nutrition, McGill University}
\affil[3]{\small Department of Mathematical and Statistical Science, University of Alberta}

@@

% Acknowledgements
\section*{Acknowledgements}
We wish to acknowledge the STEM Fellowship for organizing the 2020 Big Data Challenge, as well as Roche, SAS, Canadian Science Publishing, Digital Science, Altmetric, and Overleaf for their contributions that enabled this competition. A special thanks goes to our Big Data Challenge team members, Mehul Gupta and Sunand Kannappan. We would also like to acknowledge Stephen Styles, Danyi Liu, and Boya Peng for their critical statistical review of the manuscript draft.

\bibliographystyle{IEEEtranN}
\bibliography{bibliography}
